Browsernative Microservices

### 2017-01-04 paper.tex
pdf/tex build

In a nutshell a microservice is a small, autonomous service that works
together with other services seamlessly.{[}2, p. 2{]} or with the words
of Fowler and Lewis: ``It is an approach to developing a single
application as a suite of small services, each running in its own
process and communicating with lightweight mechanisms,\ldots{}''{[}3{]}
Microservices incorporate many ideas, like \emph{domain-driven design}
where we try to represent the real world in our code.{\textbf{???}} Or
making use of \emph{continuous delivery} for pushing software rapidly
through \emph{automated deployment} mechanisms in production.{[}3{]}
And, last but not least, microservices utilizes the idea of small teams
with a lot of product knowledge working mostly autonomous on their very
own service with their very own set of tools and techniques.

>>>>

In a nutshell a microservice is a small, autonomous service that works
together with other services seamlessly.{[}2, p. 2{]} or with the words
of Fowler and Lewis: ``It is an approach to developing a single
application as a suite of small services, each running in its own
process and communicating with lightweight mechanisms,\ldots{}''{[}3{]}
Microservices incorporate many ideas, like \emph{domain-driven design}
where we try to represent the real world in our code.{[}2, p. 2{]} Or
making use of \emph{continuous delivery} for pushing software rapidly
through \emph{automated deployment} mechanisms in production.{[}3{]}
And, last but not least, microservices utilizes the idea of small teams
with a lot of product knowledge working mostly autonomous on their very
own service with their very own set of tools and techniques.
